Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-03-30 parts/figures.tex
updated table and desc
edited stelmass

\begin{figure*}
\inclGrid{spl-input}
\caption{Nine of the lens candidates marked up with spaghetti
  diagrams.  Red, blue and green dots are proposed locations for
  maxima, minima and saddle points of the arrival time respectively.

	The curves
  help guide the placement of the dots, but their precise appearance
  has no significance.  This selection includes the best-modelled
  systems, but also one case (SW57 at upper right) of unsuccessful
  modelling.  Since the modelling process is collaborative among the
  volunteers, with anyone welcome to contribute new models or modify
  existing ones, there are variant spaghetti diagrams for all the
  modelled systems.  The online supplement displays all the models
  presented for discussion during this work.
\label{fig:splinput}}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{Total mass in the model against the estimated stellar mass,
  alongside the values for the whole sample.  (The labelled orange
  bars are the systems shown in detail in
  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The lower-right shaded
  region is unphysical according to the stellar-population models,
  because it gives $M<\Mstel$. The upper-left shaded region is
  unphysical according to abundance matching (see
  Section~\ref{sec:stellar-mass}) because it gives $M>\Mhalo$.  That
  is to say, the unshaded region is
  $0<\haloindex<1$. \label{fig:stelmass}}
\end{figure*}

\begin{table*}
  \caption{Categorisation of SW models}
  \label{tab:models}
  \include{parts/table}
\end{table*}

>>>>

\begin{figure*}
\inclGrid{spl-input}
\caption{Nine of the lens candidates marked up with spaghetti
  diagrams.  Red, blue and green dots are proposed locations for
  maxima, minima and saddle points of the arrival time respectively.
  The curves help guide the placement of the dots, but their precise
  appearance has no significance.  This selection includes the
  best-modelled systems, but also one case (SW57 at upper right) of
  unsuccessful modelling.  Since the modelling process is
  collaborative among the volunteers, with anyone welcome to
  contribute new models or modify existing ones, there are variant
  spaghetti diagrams for all the modelled systems.  The online
  supplement displays all the models presented for discussion during
  this work.
\label{fig:splinput}}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\linewidth]{img/mlens_vs_mstel_one/mstel_vs_mtot_one}
\caption{Total mass in the model against the estimated stellar mass,
  alongside the values for the whole sample.  (The labelled orange
  bars are the systems shown in detail in
  Figures~\ref{fig:splinput}--\ref{fig:encl}.)  The horizontal and
  vertical extents of each bar indicate the uncertainties in the
  stellar and total masses.  The lower-right shaded region is
  unphysical according to the stellar-population models, because it
  gives $M<\Mstel$. The upper-left shaded region is unphysical
  according to abundance matching (see Section~\ref{sec:stellar-mass})
  because it gives $M>\Mhalo$.  That is to say, the unshaded region is
  $0<\haloindex<1$. \label{fig:stelmass}}
\end{figure*}

\begin{table*}
  \caption{Diagnostics of a selected model for each Space Warps candidate
    (see Section~\ref{sec:summary}).}
  \label{tab:models}
  \include{parts/table}
\end{table*}

### 2017-03-30 parts/stelmass.tex
todo for PS
edited stelmass

In this paper we further simplify the analysis by assuming a
relationship between the apparent total magnitude and stellar mass, at
the redshift of the lens.  For typical stellar population parameters,
the variation of this relation is at most 1\,dex.  A further possible
systematic error is contamination of the light of the lensing galaxy
by the lensed background galaxy.  Reducing or eliminating the latter would
require detailed fitting of light distributions for each candidate
\citep[see][]{2011ApJ...740...97L}, which we have not yet attempted.  These 
caveats notwithstanding, it is still interesting to compare the derived
stellar mass with the lensing mass.

@@

In addition, we also derive halo masses for the lenses by use of the
standard abundance matching technique, whereby a comparison of the
observed stellar mass function of galaxies with the dark matter halo
mass function from $N$-body simulations results in a simple relation
between the two. We emphasize that this derivation of halo mass should
be considered an ``average'' estimate, and a significant scatter can
be expected as galaxies with the same stellar mass can be found in
different environments. We refer the reader to \cite{2012MNRAS.424..104L}
for an assessment of the effect of abundance matching on the
derivation of dark matter halo properties in lensing galaxies. We
follow the prescription of \citet{2010ApJ...710..903M}, namely:
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma} \\
C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
Figure~\ref{fig:stelmass} may be compared with Figure~4 in
\cite{2011ApJ...734...69M}.

>>>>

In this paper we further simplify the analysis by assuming a
relationship between the apparent total magnitude and stellar mass, at
the redshift of the lens.  For typical stellar-population parameters,
the variation of this relation is at most 1\,dex.  A further possible
systematic error is contamination of the light of the lensing galaxy
by the lensed background galaxy.  Reducing or eliminating the latter
would require detailed fitting of light distributions for each
candidate \citep[see][]{2011ApJ...740...97L}, which we have not yet
attempted.  Nonetheless, because the lensing masses range over two
order of magnitude, it is still interesting to compare with very rough
stellar masses.

@@

In addition, we also derive halo masses for the lenses using an
abundance-matching formula.  This technique matches the distribution
function of observed stellar mass in galaxies with that of dark-halo
masses in $N$-body simulations to derive simple relation between
stellar mass and halo mass.  We emphasize that a halo mass from
abundance matching should be considered an ``average'' estimate, and a
significant scatter can be expected as galaxies with the same stellar
mass can be found in different environments. We refer the reader to
\cite{2012MNRAS.424..104L} for an assessment of the effect of
abundance matching on the derivation of dark matter halo properties in
lensing galaxies. We follow the prescription of
\citet{2010ApJ...710..903M}, namely:
\begin{equation}
\begin{aligned}
\frac{\Mstel}{\Mhalo} &= \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma} \\
C_0 &= 0.02820, \quad M_1 = 10^{11.884} M_\odot \\
\beta &= 1.057, \quad \gamma = 0.556.
\end{aligned}
\end{equation}
Figure~\ref{fig:stelmass} may be compared with Figure~4 in
\cite{2011ApJ...734...69M}.
